Plot Results

### 2020-02-07 code/ResultsPlots.Rmd
again

```{r PushToSynapse,include=FALSE}

>>>>

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'TWAS Results';
activityDescription = 'Results Plots from TWAS Analysis';
thisFileName <- 'ResultsPlots.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'TWAS Results';
activityDescription = 'Results Plots from TWAS Analysis';
CODE <- syn_temp$store(synapseclient$Folder(name = "TWAS Results Figures", parentId = parentId))

#Set Used SynIDs For Provenance
#Syns_Used <- c("")

# Set annotations
all.annotations = list(
  dataType = 'pdf',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'TWAS',
  study = 'TWAS', 
  organism = 'HomoSapiens',
  consortium	= c( 'ROSMAP', 'MSBB','Mayo' ),
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  genomeAssemblyID = 'GRCh37'
)

#TODO add provenance used = Syns_Used,

# Store SVA results
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.pdf', name = 'Twas Gene Association Manhattan Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Manhattan Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_qq.pdf', name = 'Twas Gene Association QQ-Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'QQ-Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
